Poseidon Adventure

### 2019-05-24 docs/index.Rmd

@@

>>>>

May 24: Sardines have a full dataset, but still working on converting to true ages for species with multiple ages per age class. See below under [True age compositions].

@@

### True age compositions

<a href="https://sgaichas.github.io/poseidon-dev/FullBoccaccioTruthEx.html" target="_blank">Initial testing of true age functions, now running but output wrong - May 24, 2019</a>
